Generality in food webs scales with species richness, not latitude

### 2015-05-18 manuscript/latitudepaper.tex
found a couple more refs

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities \citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
  such as habitat type \citep{Shurin2006,Briand1983}, primary productivity \citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes \citep{mappaper}. These variables affect both the resources available and species' 
  metabolisms~\citep{,Hechinger2011}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,Macpherson2002,Kaufman1995}.

>>>>

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities \citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
  such as habitat type \citep{Shurin2006,Briand1983}, primary productivity \citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes \citep{mappaper}. These variables affect both the resources available and species' 
  metabolisms~\citep{,Hechinger2011}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}.
